r5r: Rapid Realistic Routing with R5 in R

### 2020-09-17 r-package/paper2020/paper2020.Rmd
fixes comments in paper

#> Examples of similar papers
#> - https://transportfindings.org/article/8416-accessibility-toolbox-for-r-and-arcgis
#> 
#> - https://transportfindings.org/article/6945-dodgr-an-r-package-for-network-flow-aggregation
#> 
#> - https://joss.theoj.org/papers/10.21105/joss.01926

@@

#> Rafa's notes
#> jean: #>-  mass of assumptions regarding decision-making and routing (Miller, 2018). 
#>Haugen, 2011; Schwanen, 2008
#>
#>Miller, E.J., 2018. Accessibility: measurement and application in transportation planning. Transp. Rev. 38, #>551–555. https://doi.org/10.1080/01441647.2018.1492778
#>
#>This article presents **r5r**, a new open-source `R` package for rapid 
#>realistic routing on multimodal transport networks.

>>>>

<!-- Examples of similar papers -->
<!--  - https://transportfindings.org/article/8416-accessibility-toolbox-for-r-and-arcgis -->

<!--  - https://transportfindings.org/article/6945-dodgr-an-r-package-for-network-flow-aggregation -->

<!--  - https://joss.theoj.org/papers/10.21105/joss.01926 -->

@@

<!-- Rafa's notes -->
<!-- jean: #>-  mass of assumptions regarding decision-making and routing (Miller, 2018).  -->
<!-- Haugen, 2011; Schwanen, 2008 -->

<!-- Miller, E.J., 2018. Accessibility: measurement and application in transportation planning. Transp. Rev. 38, #>551–555. https://doi.org/10.1080/01441647.2018.1492778 -->

<!-- This article presents **r5r**, a new open-source `R` package for rapid  -->
<!-- realistic routing on multimodal transport networks. -->
